Bootstrap Confidence Intervals for Sharp Regression Discontinuity Designs

### 2016-08-12 main_paper.tex
Update the text in simulation section
It is updated because:
1. the heteroskedastic DGP is changed.
2. the option for variance estimator in analytical procedures is
changed.

We include two other procedures for comparison: CCT's bias-corrected interval
and a ``naive'' uncorrected estimator, both using the triangular kernel. We
estimate CCT's bias corrected procedure with AMSE-optimal bandwidth and estimate
the ``naive'' uncorrected interval with the optimal bandwidth $h$ proposed by
\cite{IK}, and both use the HC3 variance estimator to facilitate comparisons
with the Wild bootstrap.\footnote{%
  Simulation results for other kernels and variance estimators are similar and
  available upon request.} %

@@

The column ``CI Coverage'' lists the experimental coverage of each interval.  In
Panel A, all of the intervals from two robust estimators are reasonably close to
their nominal coverage, although they slightly under cover the true treatment
effect. The uncorrected intervals perform substantially worse---the naive
analytical interval has coverage as bad as 35\% (in the second DGP) and never
higher than 86\%. In Panel B, the coverage does not change too much from Panel
A. In presence of heteroskedasticity, the two robust procedures again perform
similarly and have coverage close to the nominal level. The final column, ``CI
Length,'' indicates that intervals from the two robust procedures have almost
the same length on average, while interval from the naive procedure has much
shorter length on average. Not surprisingly, the average length of intervals
from all three procedures increases when the data is heteroskedastic.

>>>>

We include two other procedures for comparison: CCT's bias-corrected interval
and a ``naive'' uncorrected estimator. We
estimate CCT's bias corrected procedure with AMSE-optimal bandwidth and estimate
the ``naive'' uncorrected interval with the optimal bandwidth $h$ proposed by
\cite{IK}. We use triangular kernel through out all the three procedures to facilitate direct comparisons.\footnote{%
Simulation results for other kernels and variance estimators are similar and
available upon request.} %

@@

The column ``CI Coverage'' lists the experimental coverage of each interval.  In
Panel A, all the intervals from two robust estimators are reasonably close to
their nominal coverage, although they slightly under cover the true treatment
effect. Our proposed bootstrap procedure consistently performs well, as it is about a percentage point closer to nominal coverage than the analytically-corrected interval. The uncorrected interval performs substantially worse---the naive
analytical interval has coverage as bad as 31\% (in the second DGP) and never
higher than 86\%. In Panel B, the coverage does not change too much from Panel
A. It slightly increases in DGP 1 and decreases in DGP 2 and 3 for all three procedures. In presence of heteroskedasticity, the two robust procedures again perform
similarly and have coverage close to the nominal level. The final column, ``CI
Length,'' indicates that intervals from the two robust procedures have average lengths close to each other, while interval from the naive procedure has much
shorter length on average. Not surprisingly, the average length of intervals
from all three procedures increases when the data is heteroskedastic.
